\textbf{How open are hybrid journals included in transformative agreements?}

### 2024-09-11 analysis/manuscript.Rmd
Reviewer 1: Make description of CC and ROR-ID retrieval and journal inclusion clearer

Open access articles in hybrid journals were identified using the Creative Commons (CC) license information in Crossref metadata. 
License information relative to the "accepted manuscript (AM)" version was not considered. 
Crossref was used for open access identification because transformative agreement workflows generally require publishers to deliver CC license information to this DOI registration agency [@Geschuhn_2017].

@@

To estimate the impact of transformative agreements on hybrid open access, participating institutions from the Transformative Agreement Data dump, which the cOAlition S crowd-sourced from  agreement documents and consortia, were matched with the first author affiliations recorded by OpenAlex using the ROR-ID.
Matching also considered the duration of agreements according to the ESAC registry.
Upon inspection, Transformative Agreement Data did not comprehensively cover associated institutions, such as university hospitals or institutes of large research organisations such as the Max Planck Society.
To improve the matching, Transformative Agreement Data were automatically enriched with associated organisations using OpenAlex's institution entity data.

The so compiled data set consists of `r hoaddata::jn_ind |> filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |> distinct(issn_l, cr_year, jn_all) |> pull(jn_all) |> sum()` articles published in `r hoaddata::jn_ind |> filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |> distinct(issn_l) |> nrow()` hybrid journals between 2018 and 2022 (see Figure \ref{fig:method_fig}B). 
Hybrid journals in transformative agreements represented `r cr_stats |> filter(src == "hoad") |> pull(n_articles) |> sum() / cr_stats |> pull(n_articles) |> sum() * 100`%  of the total global output over the same time period, according to Crossref, while fully open access journals recorded 
`r cr_stats |> filter(is.na(src) & oa_status == "gold") |> pull(n_articles) |> sum() / cr_stats |> pull(n_articles) |> sum() * 100`%.

>>>>

Open access articles in hybrid journals were identified using the Creative Commons (CC) license information in Crossref metadata, with consideration of any CC variant. 
License information relative to the "accepted manuscript (AM)" version was not considered. 
Crossref was used for open access identification because transformative agreement workflows generally require publishers to deliver CC license information to this DOI registration agency [@Geschuhn_2017].

@@

To estimate the impact of transformative agreements on hybrid open access, participating institutions from the Transformative Agreement Data dump, which the cOAlition S crowd-sourced from  agreement documents and consortia, were matched with the first author affiliations recorded by OpenAlex using the ROR-ID.
Matching also considered the duration of agreements according to the ESAC registry.
Upon inspection, Transformative Agreement Data did not comprehensively cover associated institutions, such as university hospitals or institutes of large research organisations such as the Max Planck Society.
To improve the matching, Transformative Agreement Data were automatically enriched with ROR-IDs from associated organisations according to OpenAlex's institution entity data.

The so compiled data set consists of `r hoaddata::jn_ind |> filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |> distinct(issn_l, cr_year, jn_all) |> pull(jn_all) |> sum()` articles published in `r hoaddata::jn_ind |> filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |> distinct(issn_l) |> nrow()` hybrid journals included in at least one transformative agreement between 2018 and 2022 (see Figure \ref{fig:method_fig}B). 
These hybrid journals in transformative agreements represented `r cr_stats |> filter(src == "hoad") |> pull(n_articles) |> sum() / cr_stats |> pull(n_articles) |> sum() * 100`%  of the total global output over the same time period, according to Crossref, while fully open access journals recorded 
`r cr_stats |> filter(is.na(src) & oa_status == "gold") |> pull(n_articles) |> sum() / cr_stats |> pull(n_articles) |> sum() * 100`%.
